Genome-wide changes in expression during inflorescence architecture development

### 2015-08-21 ms.Rmd
writing

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("png", "cairo_pdf"),
               fig.width=3.150,
               fig.height=6.3,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

### Running title

### Keywords

### SRA details for libaries

@@

***

@@

```{r f_mfuzzClusters, fig.height=6.3}
print(f_mfuzzClusters)
```

@@

```{r f_gsea}
print(f_gsea)
```

@@

***

@@

***

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("png", "cairo_pdf"),
               fig.width=3.150,
               fig.height=8.661,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

## Running title

## Keywords

## SRA details for libaries

@@

@@

```{r f_mfuzzClusters, fig.height = 8.661 / 2}
print(f_mfuzzClusters)
```

@@

```{r f_gsea, fig.height = 8.661 / 2}
print(f_gsea)
```

@@

```{r pander, results = "asis"}
pander::set.alignment('left', row.names = 'right')
pander::set.caption(paste0(
  I(pasteLabel("**Table ", tableCount, "t_hypergeom")),
  '**: Transcription factor family enrichment per cluster'))
pander::pandoc.table(t_hypergeom, split.tables = Inf, emphasize.rownames = FALSE)
```

@@

# `R sessionInfo()` (*hide*)

```{r sessionInfo, results = "asis"}
pander::pander(sessionInfo())
git <- c(paste("**git branch:**",system("git rev-parse --abbrev-ref HEAD", intern = TRUE)),
          paste("**git hash:**", system("git rev-parse HEAD", intern = TRUE)))

for (x in git){cat(x, "\n")}
